---
title: "step10_analysis"
author: "luozhihui"
date: "2019/8/27"
output: 
  html_document:
    code_folding: show
    highlight: haddock
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)
```

## Load data
First, we need to load R library, data file ,and R function  

```{r load related data, echo=FALSE, results='hide'}
source("step9_DEG_chip_gene.R")

```

## For RNA
show the RNA differential expression data
diff_gene_in_mouse has 4 parameters:
1. dataframe
2. column 1
3. column 2
4. log2 fold change
5. gene ID

```{r RNA data}
mark = ""
state = ""
summary_rna = Summary_data(mark, state, diff_gene_in_mouse, "RNA")
summary_rna$total_table
```






## For one mark
for each mark we can run this chunck
enhancer
```{r enhancer data}
#read one mark
mark = "H3K27ac"
state = "enhancer"
summary_enhancer = Summary_data(mark, state, diff_gene_for_chip, "Chip")
summary_enhancer$total_table
```
promoter
```{r promoter data}
mark = "H3K4me3"
state = "promoter"
summary_promoter = Summary_data(mark, state, diff_gene_for_chip, "Chip")
summary_promoter$total_table
```
repressed
```{r repressed data}
mark = "H3K27me3"
state = "repressed"
summary_repressed = Summary_data(mark, state, diff_gene_for_chip, "Chip")
summary_repressed$total_table

```
heterochromatin
```{r heterochromatin data}
mark = "H3K9me3"
state = "heterochromatin"
summary_heterochromatin = Summary_data(mark, state, diff_gene_for_chip, "Chip")
summary_heterochromatin$total_table
```

## Hypergeometric test for RNA and one mark
```{r, Hypergeometric test}
data_enhancer = enrichment(summary_rna, summary_enhancer, "H3K27ac")
data_enhancer
data_promoter = enrichment(summary_rna, summary_promoter, "H3K4me3")
data_promoter
data_repressed = enrichment(summary_rna, summary_repressed, "H3K27me3")
data_repressed
data_heterochromatin = enrichment(summary_rna, summary_heterochromatin, "H3K9me3")
data_heterochromatin

```
## two marker and RNA identity
在这个部分，主要可以看两个histone信号一致的基因有哪些  
marker的一致指的是：  
enhancer 上调，promoter 上调， RNA上调  
enhancer 上调，repressed 下调， RNA上调  
enhancer 上调，heterochromatin 下调， RNA上调  
promoter上调， repressed下调， RNA上调  
promoter上调， heterochromatin下调， RNA上调  
repressed下调，heterochromatin下调， RNA上调  
这些都算一致，并且会在state状态里面标up，up指的是基因的表达上调了  
反之也是一样
表格里的列名如下：two_mark, state, up_down, geneID, symbol, withRNA  
two_mark：指的是哪两种histone marker在差异表达上是一致的
state：有三个取值cancer（表示在7week 和 10week里取交集）， colits（表示在2week 和 4week 里取交集）， all（表示在所有的week里取交集）
up_down：有两个取值up（表示基因表达上调的信号改变），down（表示会让基因表达下调的改变）
geneID：ensembl ID
symbol：gene symbol
withRNA：true表示RNA的差异表达情况与表观信号差异表达一致，false表示两者不一致（有可能是RNA在这里差异表达方向相反，也可能是不差异表达）
上次在ppt里展示的几个基因是按照：two_mark：enhancer_promoter， state：all， up_down：up和down都有， withRNA：true，挑选出来的
### enhancer and promoter
```{r 3 factor result}
#print(length(down_enhancer_promoter))
#enhancer_promoter
df_enhancer_promoter = two_mark(summary_enhancer, summary_promoter, summary_rna, "enhancer_promoter")
datatable(df_enhancer_promoter)
#enhancer_repressed
```
### enhancer and repressed
```{r enhancer and repressed}
summary_repressed_verse = reverse_list(summary_repressed)
df_enhancer_repressed = two_mark(summary_enhancer, summary_repressed_verse, summary_rna, "enhancer_repressed")
datatable(df_enhancer_repressed)
#promoter_repreesed
```
### promoter and repreesed
```{r promoter and repreesed}
df_promoter_repressed = two_mark(summary_promoter, summary_repressed_verse, summary_rna, "promoter_repressed")
datatable(df_promoter_repressed)
#enhancer_heterochromatin
```
### enhancer and heterochromatin
```{r enhancer and heterochromatin}
summary_heterochromatin_reverse = reverse_list(summary_heterochromatin)
df_enhancer_heterochromatin = two_mark(summary_enhancer, summary_heterochromatin_reverse, summary_rna, "enhancer_heterochromatin")
datatable(df_enhancer_heterochromatin)
#promoter_heterochromatin
```
### promoter and heterochromatin
```{r promoter and heterochromatin}
df_promoter_heterochromatin = two_mark(summary_promoter, summary_heterochromatin_reverse, summary_rna, "promoter_heterochromatin")
datatable(df_promoter_heterochromatin)
#repressed_heterochromatin
```
### repressed and heterochromatin
```{r repressed and heterochromatin}
df_repressed_heterochromatin = two_mark(summary_repressed_verse, summary_heterochromatin_reverse, summary_rna, "repressed_heterochromatin")
datatable(df_repressed_heterochromatin)
```


## GWAS gene
```{r GWAS data}
path_gwas = "/home/zhihl/Project/CRC/Chip_analysis/peak_dir_0821/gwas_gene/gene_list.txt"
CRCgwasList = as.vector(read.delim(path_gwas, sep = "\t", header=F)$V1)

cols <- c("SYMBOL", "ENTREZID", "ENSEMBL")
library(org.Hs.eg.db)
up_cancer_gwas = intersect(CRCgwasList, mouse2human(summary_promoter$commom_cancer_list[[1]]))
down_cancer_gwas = intersect(CRCgwasList, mouse2human(summary_promoter$commom_cancer_list[[2]]))
up_colits_gwas = intersect(CRCgwasList, mouse2human(summary_promoter$commom_colits_list[[1]]))
down_colits_gwas = intersect(CRCgwasList, mouse2human(summary_promoter$commom_colits_list[[2]]))


print(length(up_cancer_gwas))
symbol = AnnotationDbi::select(org.Hs.eg.db, keys=as.vector(up_cancer_gwas), columns=cols, keytype="ENSEMBL")
print(symbol)
print(length(down_cancer_gwas))
print(length(up_colits_gwas))
symbol = AnnotationDbi::select(org.Hs.eg.db, keys=as.vector(up_colits_gwas), columns=cols, keytype="ENSEMBL")
print(symbol)
print(length(down_colits_gwas))


#enhancer
up_cancer_gwas = intersect(CRCgwasList, mouse2human(summary_enhancer$commom_cancer_list[[1]]))
down_cancer_gwas = intersect(CRCgwasList, mouse2human(summary_enhancer$commom_cancer_list[[2]]))
up_colits_gwas = intersect(CRCgwasList, mouse2human(summary_enhancer$commom_colits_list[[1]]))
down_colits_gwas = intersect(CRCgwasList, mouse2human(summary_enhancer$commom_colits_list[[2]]))



symbol = AnnotationDbi::select(org.Hs.eg.db, keys=as.vector(up_cancer_gwas), columns=cols, keytype="ENSEMBL")
print(length(up_cancer_gwas))
print(symbol)


symbol = AnnotationDbi::select(org.Hs.eg.db, keys=as.vector(down_cancer_gwas), columns=cols, keytype="ENSEMBL")
print(length(down_cancer_gwas))
print(symbol)

symbol = AnnotationDbi::select(org.Hs.eg.db, keys=as.vector(up_colits_gwas), columns=cols, keytype="ENSEMBL")
print(length(up_colits_gwas))
print(symbol)

symbol = AnnotationDbi::select(org.Hs.eg.db, keys=as.vector(down_colits_gwas), columns=cols, keytype="ENSEMBL")
print(length(down_colits_gwas))
print(symbol)
```

## cmap
```{r cmap data}
df_all = read.delim("/home/zhihl/Project/CRC/RNA_analysis/all_diff_data.txt",sep = "\t", header=T)
col_1 = "log2FoldChange.tumorVSctrl"
col_2 = "padj.tumorVSctrl"
week_df = df_all[,c(col_1, col_2)]
cancer_df = week_df[week_df$padj.tumorVSctrl < 0.01,]
can_df = cancer_df[order(cancer_df$log2FoldChange.tumorVSctrl),]
cols <- c("SYMBOL", "ENTREZID", "ENSEMBL")
symbol = AnnotationDbi::select(org.Hs.eg.db, keys=as.vector(mouse2human(row.names(head(can_df, 400)))), columns=cols, keytype="ENSEMBL")
up_gene = symbol[,"SYMBOL"]
#write.table(up_gene , "cancer_up.txt", sep="\n", quote=F, row.names=F, col.names = F, na="NA", eol="\n")
symbol = AnnotationDbi::select(org.Hs.eg.db, keys=as.vector(mouse2human(row.names(tail(can_df, 400)))), columns=cols, keytype="ENSEMBL")
down_gene = symbol[,"SYMBOL"]
#write.table(down_gene , "cancer_down.txt", sep="\n", quote=F, row.names=F, col.names = F, na="NA", eol="\n")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
#plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
